---
title: "Test Code for App"
author: "Rachel Keller"
date: "11/9/2020"
output: html_document
---

Read in packages
```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
library(caret)
```

Read in data
```{r}
starData <- read_csv("stars.csv")
starData$`Star type` <- as.factor(starData$`Star type`)
```

Data exploration
Numeric summaries
One way table for categorical variables
```{r}
kable(table(starData$`Star color`))
```

Two way table for categorical variables
```{r}
kable(table(starData$`Star color`, starData$`Star type`))
```

Five number summary for one quantitative variable
```{r}
summary(starData$Temperature)
```

Correlation for two quantitative variables
```{r}
cor(starData$Temperature, starData$Luminosity)
```

Covariance for two quantiative variables
```{r}
cov(starData$Temperature, starData$Luminosity)
```

Graphic summaries
Barplot for one categorical variable
```{r}
g <- ggplot(data = starData, aes(x = `Star color`))
g + geom_bar()
```

Barplot for two categorical variables
```{r}
g <- ggplot(data = starData, aes(x = `Star color`, fill = as.factor(`Star type`)))
g + geom_bar()
```

Histogram for one quantitative variable
```{r}
g <- ggplot(data = starData, aes(x = Temperature))
g + geom_histogram()
```

Modeling
```{r}
set.seed(1)
train <- sample(1:nrow(starData), size = nrow(starData)*0.8)
test <- dplyr::setdiff(1:nrow(starData), train)
starDataTrain <- starData[train, ]
starDataTest <- starData[test, ]
```

First model: knn
```{r}
knnFit <- train(`Star type` ~ ., data = starDataTrain,
method = "knn",
trControl = trainControl(method = "repeatedcv", repeats = 3),
preProcess = c("center", "scale"))
```

```{r}
pred <- predict(knnFit, newdata = starDataTest)
confusionMatrix(pred, starDataTest$`Star type`)
```

Second model: random forest
```{r}
treeFit <- train(`Star type` ~ ., data = starDataTrain,
method = "rf",
trControl = trainControl(method = "repeatedcv", repeats = 3),
preProcess = c("center", "scale"))
```

```{r}
pred <- predict(treeFit, newdata = starDataTest)
confusionMatrix(pred, starDataTest$`Star type`)
```

